---
title: "Problem Set 1"
author: "Alon Rashty"
date: "04/04/2021"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 2
    toc_float: yes
    code_folding: show
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## About the Course

### Question 1
Because we need to identify the causal factor in order to apply the research results on policy-making, otherwise we could "tackle" the wrong factor and not get the results we aimed for. Causal inference is not ML main goal, and instead it is interested in the best predictions.

### Question 2
Interpreting regressions results as causal requires a valid theoretical model: We need to have (or to assume) the error is not correlated with the covariates (omitted variables), so we don't have biased estimates. Also, when we analyze experiments we need to have a good enough randomization between the treatment and control groups. 

### Question 3
* The linearity assumption means that we are looking for the average treatment effect although it might be heterogeneous.
* It means that every covariate is independent of the others, and thus we are able to investigate the effect of each one of then separately.
* Didn't understand

## The “Tidyverse”

### Question 1
```{r message=FALSE}
library(tidyverse)
library(kableExtra)
```

### Question 2
```{r results='asis'}
iris %>%
  select(contains("Sepal") | Species) %>%
  group_by(Species) %>%
  summarise("Average Sepal Length" = mean(Sepal.Length)) %>%
  kbl(align = 'lc') %>%
  kable_classic(full_width = F, html_font = "Cambria")
```


### Question 3
```{r message = FALSE}
mtcars %>%
  mutate(cyl = as.factor(cyl)) %>%
  ggplot(aes(x = hp, y = mpg, color = cyl)) +
    geom_point() +
    geom_smooth(method = lm)+
    theme(text=element_text(size=16,  family="serif"))
```

## Git & GitHub
I did it manually, but didn't understand how to put in the code itself.

